---
title: "Write Up Linear Model"
author: "Leslie Johnson"
date: "7/1/2021"
output:
    html_document:
      toc: true
      toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 

You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
## SIMS ~ ARM

###  Now add in scatterplot

```{r}
basicNN + geom_point()
```

The y-axis is SIMS, and the x-axis is ARM. This plot shows there is a positive linear correlation. There is a positive correlation between ARM and SIMS shown in this plot. 
  
###  Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The value is 0.68, a positive number that shows the line will move upwards towards the right.

###  Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The residual standard error represents the standard deviation of error points in this regression linear model and the numbers that should be considered to create the prediction equation are the estimated  coefficients. 
This equation for the prediction looks like -4.1+.05*ARM. The bigger the Adjusted R-squared the better the model.

```{r}
newdata= data.frame(GRIP = 94, ARM = 88)
predict(model.1, newdata, interval = "prediction")
```

This is a prediction interval. How far does one point vary from another if you take .7 away from 3.13. You would end up with approximately 2.3.

## SIMS ~ GRIP 
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

The equation for SIMS explained by ARM is
SIMS=4.1+.0545*ARM.
All dots traveling up are apart of that particular distribution. Every error displayed in this plot is an error. Take the distance between each point and square it. The sum of all the squared errors is the average mean error.
To find the value of SIMS multiple the intercept by -4.095160 and the ARM value 0.054563.

```{r}
basicGG <- ggplot(data,aes(y=SIMS,x=GRIP))
```
###  Now add in scatterplot

```{r}
basicGG + geom_point()
```
 
 
  
###  Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation is 0.63. This correlation is a bit smaller than the previous correlation between ARM.  

###  Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict(model.2, newdata, interval= "prediction")
```

The Adjusted R-squared is 0.4053. Previously the number was 0.409
Small standard error makes a successful model. This model is not as good as model 1 with ARM because the standard deviation is larger.

 # now add the model fit to our plot
  




  




##  SIMS ~ ARM + GRIP
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict(model.3, newdata, interval= "prediction")
```
SIMS = 5.43 + 0.37 * ARM + 0.024 * GRIP

```{r}
anova(model.1, model.3)
```

The evaluation for the line that fits this is SIMS is equal to -4.1 + 0.5 * ARM

## Model comparison

### model.1 with model.3 

model.1 and model. 3 are nested   

### model.1 with model.2

Model 2 is better than model 1 because more errors were corrected.

### model.2 with model.3

model 2 is nested in model 3, the components in model 2 are also in model 3  




