---
title: "Write Up Linear Model"
author: "Leslie Johnson"
date: "7/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 

You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```
  
# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The value is 0.58, a positive number that shows the line will move upwards towards the right.

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

This equation for the prediction looks like -4.1+.05*ARM. The bigger the Adjusted R-squared the better the model.

```{r}
newdata= data.frame(GRIP = 94, ARM = 88)
predict(model.1, newdata, interval = "prediction")
```


 # now add the model fit to our plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

The equation for SIMS explained by ARM is
SIMS=4.1+.0545*ARM. Every error displayed in this plot is an error. Take the distance between each point and square it. The sum of all the squared errors is the average mean error.

```{r}
basicGG <- ggplot(data,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicGG + geom_point()
```
 
 
  
# Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

# Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict(model.2, newdata, interval= "prediction")
```

 # now add the model fit to our plot
  




  




# Inferential  (Build linear model)
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict(model.3, newdata, interval= "prediction")
```
SIMS = 5.43 + 0.37 * ARM + 0.024 * GRIP

```{r}
anova(model.1, model.3)
```

The evaluation for the line that fits this is SIMS is equal to -4.1 + 0.5 * ARM
